### 2020-05-15 referee_responses/submission1/referee_response.tex

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
\newenvironment{myquotation}{
\begin{quotation}
\itshape
}{ 
\end{quotation}
}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Emmanuel,
$\,$\newline

\begin{singlespace}
We return our revised manuscript, ``Convective dynamics with mixed temperature boundary conditions: why thermal relaxation matters and how to accelerate it.'' 
We thank the referees for their time and effort in reviewing our work; we would like to particularly thank referee 1 for their careful and thoughtful comments.
We have addressed the questions and concerns of the referees, and we rebut the claim of referee 2 that our results are not novel.

This version of the manuscript has been substantially edited and logically reorganized compared to the previous version.
However, the main results, conclusions, and figures are largely the same.
We would like to point out a few major changes in this version of the manuscript:
\begin{enumerate}
\item The abstract has been largely rewritten for clarity.
\item The ``Simulation Details'' section has been broken up into subsections, and two new subsections have been added. These discuss:
\begin{enumerate}
\item The different initial conditions used in the simulations in this work.
The description of our TT-to-FT procedure has been moved here and expanded.
Per the advice of referee 1, we have also added and studied new ``Nu-based'' boundary conditions.
\item Evolutionary and dynamical timescales.
The text of the ``changing timescales'' section, previously in the results, has been moved here.
\end{enumerate}
\item The ``Results'' section has been broken up into two major sections.
Section III focuses on the time evolution of FT simulations which employ different initial conditions, and it compares their equilibrated states to TT simulations.
Section IV focuses on asymmetries in the flows introduced by the boundary conditions.
\item We have computed a 3D, non rotating case.
Its results are presented in section III.D, along with a new figure, Fig.~4.
\end{enumerate}
Aside from these major changes and reorganizations, we have cleaned up the text throughout the paper for clarity, including in the abstract.
We have included a ``redlined'' version of the manuscript in this resubmission which highlights the changes we have made to the text of the manuscript.

We feel that the clarity and scientific content of the paper have been greatly improved by the referee process. 
Below we include our responses to both referee reports; the original text of the reports is included in italics, and our responses follow inline in unitalicized blocks.
